---
title: "Untitled"
output: html_document
---

Read in OHI data, and save it in CSV for easy retrieval.
```{r}
library(tidyverse)
library(plotly)
df <- read.csv('https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/global2017/OHI_final_formatted_scores_2017-11-22.csv')

df %>% write_csv("/Users/richpauloo/Documents/GitHub/ohi/ohi_dat.csv")
```

Scrape Alpha-3 codes from Wikipeida for plotly (plotly_geo takes a3 codes in its `locations` argument).
```{r}
library(rvest)
http <- "https://en.wikipedia.org/wiki/ISO_3166-1_alpha-3"

region_name <- read_html(http) %>% html_nodes("td a") %>% html_text()
region_name <- region_name[1:249]

a3 <- data_frame( region_name = region_name,
                  a3_code = read_html(http) %>% html_nodes("td .monospaced") %>% html_text() )

```

Join a3 with the OHI data by region_name, and write these a3 codes to a CSV to:  

1. get a temporaty version of the data that can be used to inform the development of the app.  
2. make a template of country names that need to be manually changed  

```{r}
# write some temporary dat to play with the app before cleaning all of the a3 codes
left_join(df, a3) %>% write_csv("/Users/richpauloo/Documents/GitHub/ohi/ohi_dat_temp.csv")

# write the data frame of a3 codes to fix
left_join(df, a3) %>% 
  select(region_name, a3_code) %>% 
  distinct() %>% 
  mutate(fix = ifelse( is.na(a3_code), TRUE, "")) %>% 
  write_csv("a3_codes_fix.csv")

# write the data frame of a3 codes from wikipedia to use for fixing
a3 %>% write_csv("a3_codes_wikipeida.csv")
```

Read back in the fixed codes, append to the data for use in the final app, export the fixed data.  
```{r}
a3_fixed <- read_csv("/Users/richpauloo/Documents/GitHub/ohi/a3_codes_fixed.csv") %>% select(-fix)

# export fixed data with updated a3 codes
left_join(df, a3_fixed) %>% select(-region_id) %>% write_csv("/Users/richpauloo/Documents/GitHub/ohi/ohi_dat_clean.csv")

# export fixed 5 year change data with upated a3 codes in `lm_ohi.Rmd`
```


Test plot to verfiy that the a3 codes work.
```{r}
# light grey boundaries
l <- list(color = toRGB("grey"), width = 0.5)

# specify map projection/options
g <- list(
  showframe = FALSE,
  showcoastlines = FALSE,
  projection = list(type = 'Mercator')
)

# filter down to a grouped goal and dimension to plot
df %>% filter(goal == "AO" & dimension == "future") -> df_test
left_join(df_test, a3, by = "region_name") -> df_test

p <- plot_geo(df_test) %>%
  add_trace(
    z = ~value, color = ~value, colors = 'Blues',
    frame = ~scenario,
    text = ~region_name, locations = ~a3_code, marker = list(line = l)
  ) %>%
  colorbar(title = 'OHI score', tickprefix = '') %>%
  layout(
    title = '2014 Global GDP<br>Source:<a href="https://www.cia.gov/library/publications/the-world-factbook/fields/2195.html">CIA World Factbook</a>',
    geo = g) %>% 
  
  animation_button(
    x = 1, xanchor = "right", y = 0, yanchor = "bottom")

p
```


